Article title

### 2017-07-20 paper-webserver.tex
ADD: pts for new general 1st para

>>>>

Amongst produce in Canada, \textit{Salmonella enterica} and \textit{Escherichia coli} are the two most common bacetrial infections \cite{kozak2013foodborne}.
Translate into actual costs: hospitalization adn death \cite{thomas2015estimates}.
Of which, monetary costs have been known for decades \cite{todd1989costs}.
